\section{Introduction}

Fluids are ubiquitous in physical systems of all scales: from astronomical-scale Magnetohydrodynamics, planetary weather models, rivers and pipe-flows, to the smallest blood-vessels. Fluids can describe liquids, gases and plasmas, and appear in the limit of short mean-free-path of an \textit{N}-body problem.\\

In physics, fluids are usually described by a set of partial differential equations, which are specified according the model we choose. In the frame of an \textit{N}-body problem, we can apply different models to study different regimes. First of all, the Navier-Stokes equations predict the motion of Newtonian Fluids. They are composed of the conservations of particle, momentum, and energy, and sometimes accompanied by an equation of state. If we consider conductive fluid subeject to the electromagnetic field such as plasma, then the set of N-S equations must be associated with Maxwell's equations of electromagnetism to account for the reciprocation of the fluid and the field. Furthermore, when we consider the anisotropic transport caused by the gyromotion of magnetized plasma, then we will need to apply Braginskii's equations. The given initial conditions are often dicontinuous to the 1st order in the study of shocks and rarefaction waves with these models, which makes a Riemann problem in the classical system.\\

In this work, we want to build an \textit{N}-body solver for a set of hyperbolic advection-diffusion PDEs. To begin with, we have a preprocessor to generate the mesh and prescribe the initial conditions. Then we can set the boundary condition and select a model that applies to the problem. A robust solver is developped to accostom to the different models. And the results will be plotted by the postprocessor. This solver will be optimized to describe the fluids in different physics contexts in the frame of \textit{N}-body problem.\\
